Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-15 WSSSPE2_report/WSSSPE2_review.tex
Align tabular table

\begin{xtabular}{ll}
Jordan Adams & Tulane University\\
Alice Allen & Astrophysics Source Code Library (ASCL)\\
Gabrielle Allen & U Illinois\\
Pierre-Yves Aquilanti & TOTAL E\&P R\&T USA\\
Wolfgang Bangerth\\
David Bernholdt & Oak Ridge National Laboratory\\
Jakob Blomer\\
Carl Boettiger & UCSC/ropensci\\
Chris Bogart & ISR/CMU\\
Steven R. Brandt & Louisiana State University\\
Tom Clune & NASA GSFC\\
John W. Cobb\\
Dirk Colbry & Michigan State University\\
Karen Cranston & NESCent\\
Tom Crick & Cardiff Metropolitan University, UK\\
Ethan Davis & UCAR Unidata\\
Robert R Downs & CIESIN, Columbia University\\
Anshu Dubey & Lawrence Berkeley National Laboratory\\
Nicole Gasparini & Tulane University, New Orleans\\
Yolanda Gil & Information Sciences Institute, University of Southern California\\
Kurt Glaesemann & Pacific northwest national lab\\
Sol Greenspan &  National Science Foundation\\
Ted Habermann & The HDF Group\\
Marcus D. Hanwell & Kitware\\
Sarah Harris & University of Leeds\\
David Henty &  EPCC, The University of Edinburgh\\
Neil Chue Hong & Software Sustainability Institute \& University of Edinburgh\\
James Howison & University of Texas\\
Maxime Hughes\\
Eric Hutton &  University of Colorado\\
Ray Idaszak & RENCI/UNC\\
Samin Ishtiaq & Microsoft Research Cambridge, UK\\
Matt Jones &  University of California Santa Barbara\\
Nick Jones & New Zealand eScience Infrastructure, University of Auckland\\
Daniel S. Katz & U Chicago \& Argonne\\
Ian Kelley\\
Hilmar Lapp & National Evolutionary Synthesis Center (NESCent) and Duke University\\
Chris Lenhardt\\
Richard Littauer & MIT/University of Saarland \\
Frank L\"{o}ffler & Louisiana State University\\
Andre Luckow & Rutgers\\
Berkin Malkoc & Istanbul Technical University\\
Kyle Marcus & University of Buffalo\\
Bryan Marker & The University of Texas at Austin\\
Suresh Marru & Indiana University \\
Robert H. McDonald & Indiana University - Data to Insight Center/Libraries \\
Rupert Nash\\
Andy Nutter-Upham & Whitehead Institute\\
Abani Patra & Univ @ Buffalo\\
Aleksandra Pawlik & Software Sustainability Institute\\
Cody J. Permann & Idaho National Laboratory\\
John W. Peterson & Idaho National Laboratory\\
Benjamin Pharr & University of Mississippi\\
Stephen Piccolo &  Brigham Young University, Utah\\
Marlon Pierce & Indiana University\\
Ray Plante & NCSA/University of Illinois Urbana-Champaign\\
Sushil Prasad & Georgia State University, Atlanta \\
Karthik Ram & University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci\\
Mike Rilee\\
Mike Rilee & NASA/GSFC, Rilee Systems Technologies \\
Erin Robinson & Foundation for Earth Science \\
Mark Schildhauer &  NCEAS, Univ. California, Santa Barbara\\
Jory Schossau & Michigan State University\\
Frank Seinstra & Netherlands eScience Center\\
James Shepherd & Rice University\\
Justin Shi\\
Ardita Shkurti & University of Nottingham\\
Alan Simpson &  EPCC, The University of Edinburgh\\
Carol Song & Purdue University\\
James Spencer & Imperial College London\\
Tracy Teal & Data Carpentry\\
Kaitlin Thaney &  Mozilla Science Lab\\
Matt Turk & NCSA/UIUC\\
Colin C. Venters & University of Huddersfield\\
Nathan Weeks\\
Ethan White & University of Florida/Utah State University\\
Nancy Wilkins-Diehr & SDSC\\
Greg Wilson &  Software Carpentry\\
\end{xtabular}

>>>>

\begin{xtabular}{ll}
Jordan Adams          &  Tulane University                       \\
Alice Allen           &  Astrophysics Source Code Library (ASCL) \\
Gabrielle Allen       &  U Illinois                              \\
Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA                     \\
Wolfgang Bangerth     \\
David Bernholdt       &  Oak Ridge National Laboratory           \\
Jakob Blomer          \\
Carl Boettiger        &  UCSC/ropensci                           \\
Chris Bogart          &  ISR/CMU                                 \\
Steven R. Brandt      &  Louisiana State University              \\
Tom Clune             &  NASA GSFC                               \\
John W. Cobb          \\
Dirk Colbry           &  Michigan State University               \\
Karen Cranston        &  NESCent                                 \\
Tom Crick             &  Cardiff Metropolitan University, UK     \\
Ethan Davis           &  UCAR Unidata                            \\
Robert R Downs        &  CIESIN, Columbia University             \\
Anshu Dubey           &  Lawrence Berkeley National Laboratory                                \\
Nicole Gasparini      &  Tulane University, New Orleans                                       \\
Yolanda Gil           &  Information Sciences Institute, University of Southern California    \\
Kurt Glaesemann       &  Pacific northwest national lab                                       \\
Sol Greenspan         &  National Science Foundation                                          \\
Ted Habermann         &  The HDF Group                                                        \\
Marcus D. Hanwell     &  Kitware                                                              \\
Sarah Harris          &  University of Leeds                                                  \\
David Henty           &  EPCC, The University of Edinburgh                                    \\
Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh         \\
James Howison         &  University of Texas                                                  \\
Maxime Hughes         \\
Eric Hutton           &  University of Colorado                                               \\
Ray Idaszak           &  RENCI/UNC                                                            \\
Samin Ishtiaq         &  Microsoft Research Cambridge, UK                                     \\
Matt Jones            &  University of California Santa Barbara                               \\
Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland          \\
Daniel S. Katz        &  U Chicago \& Argonne                                                 \\
Ian Kelley            \\
Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University \\
Chris Lenhardt        \\
Richard Littauer      &  MIT/University of Saarland                                           \\
Frank L\"{o}ffler     &  Louisiana State University                                           \\
Andre Luckow          &  Rutgers                                                              \\
Berkin Malkoc         &  Istanbul Technical University                                        \\
Kyle Marcus           &  University of Buffalo                                                \\
Bryan Marker          &  The University of Texas at Austin                                    \\
Suresh Marru          &  Indiana University                                                   \\
Robert H. McDonald    &  Indiana University - Data to Insight Center/Libraries                \\
Rupert Nash           \\
Andy Nutter-Upham     &  Whitehead Institute                                                  \\
Abani Patra           &  Univ @ Buffalo                                                       \\
Aleksandra Pawlik     &  Software Sustainability Institute                                    \\
Cody J. Permann       &  Idaho National Laboratory                                            \\
John W. Peterson      &  Idaho National Laboratory                                            \\
Benjamin Pharr        &  University of Mississippi                                            \\
Stephen Piccolo       &  Brigham Young University, Utah                                       \\
Marlon Pierce         &  Indiana University                                                   \\
Ray Plante            &  NCSA/University of Illinois Urbana-Champaign                         \\
Sushil Prasad         &  Georgia State University, Atlanta                                    \\
Karthik Ram                   &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci \\
Mike Rilee                    \\
Mike Rilee                    &  NASA/GSFC, Rilee Systems Technologies                                \\
Erin Robinson                 &  Foundation for Earth Science                                         \\
Mark Schildhauer              &  NCEAS, Univ. California, Santa Barbara                               \\
Jory Schossau                 &  Michigan State University                                            \\
Frank Seinstra                &  Netherlands eScience Center                                          \\
James Shepherd                &  Rice University                                                      \\
Justin Shi                    \\
Ardita Shkurti                &  University of Nottingham                                             \\
Alan Simpson                  &  EPCC, The University of Edinburgh                                    \\
Carol Song                    &  Purdue University                                                    \\
James Spencer                 &  Imperial College London                                              \\
Tracy Teal                    &  Data Carpentry                                                       \\
Kaitlin Thaney                &  Mozilla Science Lab                                                  \\
Matt Turk                     &  NCSA/UIUC                                                            \\
Colin C. Venters              &  University of Huddersfield                                           \\
Nathan Weeks                  \\
Ethan White                   &  University of Florida/Utah State University                          \\
Nancy Wilkins-Diehr           &  SDSC                                                                 \\
Greg Wilson                   &  Software Carpentry                                                   \\
\end{xtabular}
